---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bdr

<!-- badges: start -->
<!-- badges: end -->

The goal of bdr is to provide a simple interface to interact with the 'RESTful' API of the Brown Digital Repository API https://repository.library.brown.edu/studio/api-docs/.


## Installation

You can install the released version of bdr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bdr")
```

## Example


We will use the `bdr_collections` function to grab the collections from BDR:

```{r example}
library(bdr)
df = bdr_collections()
head(df)
```

Once we have the collections, we can grab a particular collection using standard `dplyr` syntax to grab the collection you want to explore using the `bdr_collection` function:
```{r ex}
library(dplyr)
coll_url = df %>%
    filter(grepl("Bactrian ", name)) %>%
    pull(json_uri)
coll = bdr_collection(coll_url)
coll
```



We can extract the `item` URL from `coll$items`:
```{r dl}
url = coll$items[[1]]$json_uri[1]
print(url)
```

The `bdr_item_download_link` function will process links to get the download link for downloading the item:
```{r dl_link}
link = bdr_item_download_link(url)
```

We can use `httr::GET` to download the data to disk and unzip them using the `unzip` function: 
```{r dl_data}

tfile = tempfile(fileext = ".zip")
dl = httr::GET(link,
               httr::write_disk(tfile),
               if (interactive()) httr::progress())
tdir = tempfile()
dir.create(tdir)
unz = unzip(tfile, exdir = tdir)
```
